Hochschild cohomology of torus-equivariant D-modules

### 2017-05-30 paper.tex
Fixes

\newcommand\schemels[2][]{L^{#1}#2}
\newcommand\schemelsY[2][]{\schemels[#1]{_{\stack Y}#2}}
\newcommand\schemecls[2][]{\overline{L}^{#1}#2}
\newcommand\schemeclsY[2][]{\schemecls[#1]{_{\stack Y}#2}}
\newcommand\schemelsc[2][]{L^{\if\relax\detokenize{#1}\relax\else#1,\fi c} #2}
\newcommand\schemelscY[2][]{\schemelsc[#1]{_{\stack Y}#2}}

\newcommand\schemei{i'}
\newcommand\schemej{j'}
\newcommand\schemeq{q'}
\newcommand\schemebarq{\bar{q}'}
\newcommand\dropprimes{%
    \renewcommand\schemei{i}%
    \renewcommand\schemej{j}%
    \renewcommand\schemeq{q}%
    \renewcommand\schemebarq{\bar{q}}%
}
\newcommand\schemeh{h'}

@@

\newcommand\goodstack{XXXgoodXXX}
\newcommand\Goodstack{XXXGoodXXX}
\newcommand\goodness{property \textbf{(!)}}
\newcommand\goodnessshort{\textbf{(!)}}
\newcommand\isgood{has property \textbf{(!)}}
\newcommand\aregood{have property \textbf{(!)}}
\newcommand\isnotgood{does not have property \textbf{(!)}}
\newcommand\arenotgood{do not have property \textbf{(!)}}
\newcommand\goodX[1]{#1 with property \textbf{(!)}}
\newcommand\goodnessb{property \textbf{(!')}}
\newcommand\goodnessbshort{\textbf{(!')}}
\newcommand\isgoodb{has property \textbf{(!')}}
\newcommand\aregoodb{have property \textbf{(!')}}
\newcommand\goodbX[1]{#1 with property \textbf{(!')}}

@@

[$p₂$ <-> $p₁$]
[subvariety <-> subscheme]
[$Y₁$ <-> $Y₂$]
\dropprimes%
[macros]
[-advisor]
[map in contraction principle]

@@

\subsection{\Goodstack\ stacks}

@@

A similar can be used to reduce the computation to a smooth cover.
In particular we will want to reduce to computations on a schematic cover.
On such a cover we will use primes to indicate maps on schemes and will use $\schemels{}$ instead of $\ls{}$ for the covers of the loop spaces.
If we start with the cover $\bar Γ → \bar{\stack X}$, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
\begin{equation}
    \label{eq:diag:scheme-cover1}
    \begin{tikzcd}
        Γ \arrow[r, hook, "j'"] \arrow[d] &
        \bar Γ \arrow[d] &
        \scls \stack X \arrow[l, "\bar p₂'"'] \arrow[d] &
        \slsc \stack X \arrow[l, hook', "i_{\stack X}'"'] \arrow[d]\\
        %
        \stack X \arrow[r, hook, "j"] &
        \bar{\stack X} &
        \cls \stack X \arrow[l, "\bar p₂"'] &
        \lsc \stack X \arrow[l, hook', "i_{\stack X}"']
    \end{tikzcd}
\end{equation}
Similarly, the interesting parts of diagram \eqref{eq:diag:central2} become
\begin{equation}
    \label{eq:diag:scheme-cover2}
    \begin{tikzcd}
        \slsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}'"] \arrow[d] &
        \sclsY[\stack Y₂]{\stack X} \arrow[d] &
        \sclsY[\stack Y₁]{\stack X} \arrow[l, "\schemecls f"'] \arrow[d] &
        \slscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}'"'] \arrow[d]\\
        %
        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] &
        \clsY[\stack Y₂]{\stack X} &
        \clsY[\stack Y₁]{\stack X} \arrow[l, "\cls f"'] &
        \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']
    \end{tikzcd}
\end{equation}
In both diagrams all vertical morphisms are smooth and the spaces in the top row are schemes.
Explicitly, if $h'\colon Y → X$ is a $G$-equivariant morphism of schemes inducing the structure map $\stack Y → \stack X$, then
\[
    \sclsY \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
    \biggr\}.
\]

@@

The upshot of this is that we can check vanishing by restricting to all $\stabclsY[\stack Y_i]{S}{\stack X}$.
However, since these spaces are closed we will need to make use of a Mayer--Vietoris argument.
Thus we need to also consider intersections of these schemes.
For this let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$ and set
\[
    \stabclsY[\stack Y_i]{S₁,S₂} \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
    \biggr\}.
\]
Clearly we have $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \subseteq \stabclsY[\stack Y_i]{S₁}{\stack X}$ and $\stabclsY[\stack Y_i]{S}{\stack X} = \stabclsY[\stack Y_i]{S,S}{\stack X}$.
Similarly, we set
\[
    \bar Γ^{S₁,S₂} = \bigl\{ (g,x,y) ∈ \bar Γ : x ∈ X^{S₂} \text{ and there exists $g' ∈ G$ such that $g ∈ g'S₁$}  \bigr\}.
\]
As in Lemma~\ref{lem:stabilizers_cover} one sees that the closed subschemes $\bar Γ^{S,S}$ cover $\bar Γ$.
Denote the inclusions by
\[
    α_i^{S₁,S₂}\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \hookrightarrow \sclsY[\stack Y_i]{\stack X}
    \qquad\text{and}\qquad
    α_{-1}^{S₁,S₂}\colon \bar Γ^{S₁,S₂} \hookrightarrow \bar Γ.
\]
We are now ready to formulate the main technical lemma of this section.
It will allow us to cut up our spaces into pieces on which we have control over the sheaves of interest.

@@

\begin{proof}[Proof of Lemma~\ref{lem:torus:key}]
    The schemes $\stablscY[\stack Y_i]{S₁,S₂}{\stack X} = \slscY[\stack Y_i]{\stack X} ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ are given by
    \[
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
        \biggr\}.
    \]
    Set $H' = H ∩ \bar S₁$ and $Z_i' = Z_i ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$Z_{-1}' = Z_{-1} ∩ \bar Γ^{S₁,S₂}$).
    These schemes can be described as
    \[
        Z_i'
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H'
        \biggr\}.
    \]
    and similarly for $Z_{-1}'$.
    If $H' = \emptyset$ then the $Z_i'$ are empty and the statements of the lemma are trivially true.
    Thus assume that $H'$ is not empty.
    Let $i_i^{H'}$ be the inclusion of $Z_i'$ into $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$\bar Γ^{S₁,S₂}$).
    We have to show that the canonical maps
    \[
        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
        →
        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
    \]
    and
    \[
        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
        →
        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
    \]
    are isomorphisms.

>>>>

@@

\newcommand\goodness{property \textbf{(!)}}
\newcommand\goodnessshort{\textbf{(!)}}
\newcommand\isgood{has property \textbf{(!)}}
\newcommand\aregood{have property \textbf{(!)}}
\newcommand\isnotgood{does not have property \textbf{(!)}}
\newcommand\arenotgood{do not have property \textbf{(!)}}
\newcommand\goodX[1]{#1 with property \textbf{(!)}}
\newcommand\goodnessb{property \textbf{(!')}}
\newcommand\goodnessbshort{\textbf{(!')}}
\newcommand\isgoodb{has property \textbf{(!')}}
\newcommand\aregoodb{have property \textbf{(!')}}
\newcommand\goodbX[1]{#1 with property \textbf{(!')}}

@@

[$p₂$ <-> $p₁$]
[subvariety <-> subscheme]
[$Y₁$ <-> $Y₂$]
[macros]
[-advisor]
[map in contraction principle]

@@

\subsection{The !-base-change property}

@@

A similar can be used to reduce the computation to a smooth cover.
In particular we will want to reduce to computations on a schematic cover.
On such a cover we will use primes to indicate maps on schemes and will use $\sls{}$ instead of $\ls{}$ for the covers of the loop spaces.
If we start with the cover $\bar Γ → \bar{\stack X}$, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
\begin{equation}
    \label{eq:diag:scheme-cover1}
    \begin{tikzcd}
        Γ \arrow[r, hook, "j'"] \arrow[d] &
        \bar Γ \arrow[d] &
        \scls \stack X \arrow[l, "\bar p₂'"'] \arrow[d] &
        \slsc \stack X \arrow[l, hook', "i_{\stack X}'"'] \arrow[d]\\
        %
        \stack X \arrow[r, hook, "j"] &
        \bar{\stack X} &
        \cls \stack X \arrow[l, "\bar p₂"'] &
        \lsc \stack X \arrow[l, hook', "i_{\stack X}"']
    \end{tikzcd}
\end{equation}
Similarly, the interesting parts of diagram \eqref{eq:diag:central2} become
\begin{equation}
    \label{eq:diag:scheme-cover2}
    \begin{tikzcd}
        \slsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}'"] \arrow[d] &
        \sclsY[\stack Y₂]{\stack X} \arrow[d] &
        \sclsY[\stack Y₁]{\stack X} \arrow[l, "\scls f"'] \arrow[d] &
        \slscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}'"'] \arrow[d]\\
        %
        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] &
        \clsY[\stack Y₂]{\stack X} &
        \clsY[\stack Y₁]{\stack X} \arrow[l, "\cls f"'] &
        \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']
    \end{tikzcd}
\end{equation}
In both diagrams all vertical morphisms are smooth and the spaces in the top row are schemes.
Explicitly, if $h'\colon Y → X$ is a $G$-equivariant morphism of schemes inducing the structure map $\stack Y → \stack X$, then
\[
    \sclsY \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, h'(y),\, g₁h'(y)\bigr) ∈ \bar Γ
    \biggr\}.
\]

@@

The upshot of this is that we can check vanishing by restricting to all $\stabclsY[\stack Y_i]{S}{\stack X}$.
However, since these spaces are closed we will need to make use of a Mayer--Vietoris argument.
Thus we need to also consider intersections of these schemes.
For this let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$ and set
\[
    \stabclsY[\stack Y_i]{S₁,S₂} \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
    \biggr\}.
\]
Clearly we have $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \subseteq \stabclsY[\stack Y_i]{S₁}{\stack X}$ and $\stabclsY[\stack Y_i]{S}{\stack X} = \stabclsY[\stack Y_i]{S,S}{\stack X}$.
Similarly, we set
\[
    \bar Γ^{S₁,S₂} = \bigl\{ (g,x,y) ∈ \bar Γ : x ∈ X^{S₂} \text{ and there exists $g' ∈ G$ such that $g ∈ g'S₁$}  \bigr\}.
\]
As in Lemma~\ref{lem:stabilizers_cover} one sees that the closed subschemes $\bar Γ^{S,S}$ cover $\bar Γ$.
Denote the inclusions by
\[
    α_i^{S₁,S₂}\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \hookrightarrow \sclsY[\stack Y_i]{\stack X}
    \qquad\text{and}\qquad
    α_{-1}^{S₁,S₂}\colon \bar Γ^{S₁,S₂} \hookrightarrow \bar Γ.
\]
We are now ready to formulate the main technical lemma of this section.
It will allow us to cut up our spaces into pieces on which we have control over the sheaves of interest.

@@

\begin{proof}[Proof of Lemma~\ref{lem:torus:key}]
    The schemes $\stablscY[\stack Y_i]{S₁,S₂}{\stack X} = \slscY[\stack Y_i]{\stack X} ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ are given by
    \[
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
        \biggr\}.
    \]
    Set $H' = H ∩ \bar S₁$ and $Z_i' = Z_i ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$Z_{-1}' = Z_{-1} ∩ \bar Γ^{S₁,S₂}$).
    These schemes can be described as
    \[
        Z_i' =
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H'
        \biggr\}.
    \]
    and similarly for $Z_{-1}'$.
    If $H' = \emptyset$ then the $Z_i'$ are empty and the statements of the lemma are trivially true.
    Thus assume that $H'$ is not empty.
    Let $i_i^{H'}$ be the inclusion of $Z_i'$ into $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$\bar Γ^{S₁,S₂}$).
    We have to show that the canonical maps
    \[
        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
        →
        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
    \]
    and
    \[
        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
        →
        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
    \]
    are isomorphisms.
